### 2017-10-14 Chapter5/expt.tex
Latest on 15/10/2017

%We also implement the uniform-allocation (labeled UA) strategy,  CSAR is modified for the TBP setting such that it behaves as a Successive Reject algorithm whereby it rejects the arm farthest from $\tau$ after each round.
%Similarly we modify the UCBE \cite{audibert2009exploration} and UCBEV \cite{gabillon2011multi} algorithms  (originally proposed for single best arm and TopM identification problems, respectively) to suit the TBP setting. 
%%to \cite{locatelli2016optimal} to suit the goal of finding arms above the threshold $\tau$. 
%Following  \cite{locatelli2016optimal} the exploration parameter $a$ in UCBE is set to $a=\frac{T-K}{H_1}$, while for UCBEV we set $a = \frac{T-2K}{H_{\sigma,1}}$. Then, at each time-step $t=1,2,..,T$ we pull the arm that minimizes
% $\lbrace |\hat{r}_{i} -\tau|-\sqrt{\frac{a}{n_{i}}} \rbrace$, where $a$ is set as mentioned above for UCBE and UCBEV respectively. Finally, for AugUCB we take $\rho=\frac{1}{3}$ as in  Theorem \ref{Result:Theorem:1}.

%Again, for UCBEV, following \cite{gabillon2011multi}, we modify it such that the exploration parameter $a = \frac{T-2K}{H_{\sigma,1}}$. Then for each timestep $t=1,2,..,T$ we pull the arm that minimizes $\lbrace |\hat{r}_{i} -\tau|-\sqrt{\frac{a}{n_{i}}} \rbrace$, where $n_{i}$ is the number of times the arm $i$ is pulled till $t-1$ timestep and $a$ is set as mentioned above for UCBE and UCBEV respectively. Also, APT is run with $\epsilon=0.05$, which denotes the precision with which the algorithm suggests the best set of arms and we modify CSAR as per \cite{locatelli2016optimal} such that it behaves as a Successive Reject algorithm whereby it rejects the arm farthest from $\tau$ after each phase. For AugUCB we take $\rho_{\mu}=\frac{1}{8}$ and $\rho_v=\frac{1}{3}$ as in Theorem \ref{Result:Theorem:1}. In all the testbeds AugUCB, APT, CSAR, Uniform Allocation, UCBE and UCBEV are run with the same settings as mentioned above.

\noindent
Motivated by the settings considered in \cite{locatelli2016optimal}, 
we design six different experimental scenarios that are obtained by varying the arm means and variances. 
%We conduct a set of six experiments with different reward means and variances. 
Across all experiments consists of $K=100$  arms (indexed $i=1,2,\cdots,100$) of which ${S}_\tau=\{6,7,\cdots,10\}$, where we have fixed $\tau=0.5$.
%in all the experiments, the threshold $\tau$ is set to $0.5$. %for all experiments. 
%Also, the number of arms in each experiment is $K=100$ , of which $\lbrace 6,7,8,9,10 \rbrace$ arms have their reward means above $\tau$. 
In all the experiments, each algorithm is run independently for $10000$ time-steps. At every time-step, the output set,  $\hat{S}_\tau$, suggested by each algorithm is recorded; the output is counted as an error if $\hat{S}_\tau\ne S_\tau$. In Figure~1, for each experiment, we have reported the percentage of error incurred by the different algorithms as a function of time; Error percentage is obtained by repeating each experiment independently  for $500$ iterations, and then respectively computing the fraction of errors. The details of the considered experiments are as follows.

%that is obtained by computing the fraction of errors when   The experiment is repeated for $500$ independent iterations, and the average error percentage is plotted against the $10000$ time-steps.

 %The output is considered erroneous if the correct set of arms is not $i=\lbrace 6,7,8,9,10 \rbrace$ (true for all the experiments). The error percentage over $500$ runs is plotted against $10000$ timesteps.

 %For the uniform allocation algorithm, for each $t=1,2,..,T$ the arms are sampled uniformly.

%Also we run AugUCBM with arm elimination just by mean estimation and AugUCBV with arm elimination just by variance estimation. For AugUCBM, at every timestep we pull arm that minimizes $i\in\argmin_{j\in B_{m}}\bigg\lbrace |\hat{r}_{j} - \tau | - 2c_{j}\bigg\rbrace$ while for AugUCBV we pull arm that minimizes $i\in\argmin_{j\in B_{m}}\bigg\lbrace |\hat{r}_{j} - \tau | - 2s_{j}\bigg\rbrace$.

%	The first experiment is conducted on a testbed of $100$ arms involving

@@

 The corresponding variances are $\sigma_{1:5}^{2}=0.5$ and $\sigma_{6:10}^{2}=0.6$, while $\sigma_{11:100}^{2}$ is chosen independently and uniform in the  interval $[0.38,0.42]$;
% Then $\sigma_{11:100}^{2}$ is chosen uniform randomly between $0.38-0.42$.
note that, the variances of the arms in $S_\tau$ are higher than those of the other arms.
% The means in the testbed are chosen in such a way that any algorithm has to spend a significant amount of budget to explore all the arms and variance is chosen in such a way that the arms above $\tau$ have high variance whereas arms below $\tau$ have lower variance. 
 The corresponding  results are shown in Figure \ref{Fig:budgetExpt1},
 from where we see that UCBEV, which has access to the problem complexity while being variance-aware, outperforms all other algorithm (including UCBE which also has access to the problem complexity but does not take into account the variances of the arms).  Interestingly, the performance of our AugUCB (without requiring any complexity input) is comparable with UCBEV, while it 
   % with the said parameters 
 outperforms UCBE, APT and the other non variance-aware algorithms that we have considered. 	
%AugUCBM with just mean estimation performs worse than AugUCB or AugUCBV, which have a matching performance in this setup.

\begin{figure}[th!]
    \centering
    \begin{tabular}{cc}
    \subfigure[0.32\textwidth][Expt-$1$: Arithmetic Progression (Gaussian)]
    {
    		\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
      	\begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
		grid=major,
        %clip mode=individual,grid,grid style={gray!30},
        clip=true,
        %clip mode=individual,grid,grid style={gray!30},
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
      	% UCB
		\addplot table{tbandit/results/budgetTestAP/APT12_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestAP/AugUCBV1_comp_subsampled.txt};
		%\addplot table{results/budgetTestAP/AugUCBV_1_13_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestAP/UCBEM1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestAP/UCBEMV1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestAP/SR1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestAP/UA1_comp_subsampled.txt};
		%\addplot table{results/budgetTestAP/AugUCBM12_comp_subsampled.txt};
		%\addplot table{results/budgetTestAP/AugUCBV1_comp_subsampled.txt};
      	%\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc,AugUCBM,AugUCBV}
      	\legend{APT,AugUCB,UCBE,UCBEV,CSAR,UA}
      	\end{axis}
      	\end{tikzpicture}
  		\label{Fig:budgetExpt1}
    }
    &
    \subfigure[0.32\textwidth][Expt-$2$: Geometric Progression (Gaussian)]
    {
    	\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
        %clip mode=individual,grid,grid style={gray!30},
		grid=major,
		clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
        % UCB
		\addplot table{tbandit/results/budgetTestGP/APT12_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGP/AugUCBV1_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBV_1_13_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGP/UCBEM1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGP/UCBEMV1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGP/SR1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGP/UA1_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBM12_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBV1_comp_subsampled.txt};
        %\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc,AugUCBM,AugUCBV}
        \legend{APT,AugUCB,UCBE,UCBEV,CSAR,UA}
      	\end{axis}
      	\label{Fig:budgetExpt2}
        \end{tikzpicture}
    }
    \end{tabular}

	\begin{tabular}{cc}
	\centering
    \subfigure[0.32\textwidth][Expt-$3$: Three Group Setting (Gaussian)]
    {
    		\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
        %clip mode=individual,grid,grid style={gray!30},
       	grid=major,
       	clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
      	% UCB
		\addplot table{tbandit/results/budgetTestGR1/APT1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR1/AugUCB1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR1/UCBEM1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR1/UCBEMV1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR1/SR1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR1/UA1_comp_subsampled.txt};
        \legend{APT,AugUCB,UCBE,UCBEV,CSAR,UA}
      	\end{axis}
      	\end{tikzpicture}
   		\label{Fig:budgetExpt3} 
    }
    &
    \subfigure[0.32\textwidth][Expt-$4$: Two Group Setting (Gaussian) ]
    {
    	\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
        %clip mode=individual,grid,grid style={gray!30},
		grid=major,
		clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
        % UCB
		\addplot table{tbandit/results/budgetTestGR2/APT1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR2/AugUCBV1_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBV_1_13_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR2/UCBEM1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR2/UCBEMV1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR2/SR1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR2/UA1_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBM12_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBV1_comp_subsampled.txt};
        %\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc,AugUCBM,AugUCBV}
        \legend{APT,AUgUCB,UCBE,UCBEV,CSAR,UA}
        %\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc}
      	\end{axis}
      	\label{Fig:budgetExpt4}
        \end{tikzpicture}
    }
    \end{tabular}

	\begin{tabular}{cc}
    \subfigure[0.32\textwidth][Expt-$5$: Two Group Setting (Advance) ]
    {
    	\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
        %clip mode=individual,grid,grid style={gray!30},
		grid=major,
		clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
        % UCB
		\addplot table{tbandit/results/budgetTestGR4/APT1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR4/AugUCB1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR4/UCBEM1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR4/UCBEMV1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR4/SR1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR4/UA1_comp_subsampled.txt};
        \legend{APT,AUgUCB,UCBE,UCBEV,CSAR,UA}
      	\end{axis}
      	\label{Fig:budgetExpt5}
        \end{tikzpicture}
    }
    &
    \subfigure[0.32\textwidth][Expt-$6$: Two Group Setting (Advance) ]
    {
    	\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
        %clip mode=individual,grid,grid style={gray!30},
		grid=major,
		clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=2} ]
        % UCB
		\addplot table{tbandit/results/budgetTestGR3/testUCBEMV1_0.25_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR4/AugUCB1_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBV_1_13_comp_subsampled.txt};
		%\addplot table{results/budgetTestGR3/testUCBEMV1_0.25_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR3/testUCBEMV1_256_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR4/UCBEMV1_comp_subsampled.txt};
		%\addplot table{results/budgetTestGR3/testUCBEMV1_64_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBM12_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBV1_comp_subsampled.txt};
        %\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc,AugUCBM,AugUCBV}
        \legend{UCBEV($0.25$), AugUCB, UCBEV($256$), UCBEV($1$)}
        %\legend{UCBEV($0.06$),AUgUCB,UCBEV($0.25$),UCBEV($1$),UCBEV($64$),UCBEV($256$)}
        %\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc}
      	\end{axis}
      	\label{Fig:budgetExpt6}
        \end{tikzpicture}
    }
    \end{tabular}
    \caption{Performances of the various TBP algorithms in terms of error percentage vs. time-step, for  six different experimental scenarios.}
    \label{fig:budgetExpt}
    \vspace{-6mm}
\end{figure}

>>>>

\noindent
Motivated by the settings considered in \cite{locatelli2016optimal}, 
we design six different experimental scenarios that are obtained by varying the arm means and variances.  Across all experiments consists of $K=100$  arms (indexed $i=1,2,\cdots,100$) of which ${S}_\tau=\{6,7,\cdots,10\}$, where we have fixed $\tau=0.5$. In all the experiments, each algorithm is run independently for $10000$ time-steps. At every time-step, the output set,  $\hat{S}_\tau$, suggested by each algorithm is recorded; the output is counted as an error if $\hat{S}_\tau\ne S_\tau$. In Figure~1, for each experiment, we have reported the percentage of error incurred by the different algorithms as a function of time; Error percentage is obtained by repeating each experiment independently  for $500$ iterations, and then respectively computing the fraction of errors. The details of the considered experiments are as follows.

@@

 The corresponding variances are $\sigma_{1:5}^{2}=0.5$ and $\sigma_{6:10}^{2}=0.6$, while $\sigma_{11:100}^{2}$ is chosen independently and uniform in the  interval $[0.38,0.42]$; note that, the variances of the arms in $S_\tau$ are higher than those of the other arms. The corresponding  results are shown in Figure \ref{Fig:budgetExpt1}, from where we see that UCBEV, which has access to the problem complexity while being variance-aware, outperforms all other algorithm (including UCBE which also has access to the problem complexity but does not take into account the variances of the arms).  Interestingly, the performance of our AugUCB (without requiring any complexity input) is comparable with UCBEV, while it outperforms UCBE, APT and the other non variance-aware algorithms that we have considered.

\begin{figure}[th!]
    \centering
    \begin{tabular}{cc}
    \subfigure[0.32\textwidth][Expt-$1$: Arithmetic Progression (Gaussian)]
    {
    		\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
      	\begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
		grid=major,
        %clip mode=individual,grid,grid style={gray!30},
        clip=true,
        %clip mode=individual,grid,grid style={gray!30},
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
      	% UCB
		\addplot table{Chapter5/results/budgetTestAP/APT12_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestAP/AugUCBV1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestAP/UCBEM1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestAP/UCBEMV1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestAP/SR1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestAP/UA1_comp_subsampled.txt};

      	\legend{APT,AugUCB,UCBE,UCBEV,CSAR,UA}
      	\end{axis}
      	\end{tikzpicture}
  		\label{Fig:budgetExpt1}
    }
    &
    \subfigure[0.32\textwidth][Expt-$2$: Geometric Progression (Gaussian)]
    {
    	\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
        %clip mode=individual,grid,grid style={gray!30},
		grid=major,
		clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
        % UCB
		\addplot table{Chapter5/results/budgetTestGP/APT12_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGP/AugUCBV1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGP/UCBEM1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGP/UCBEMV1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGP/SR1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGP/UA1_comp_subsampled.txt};
        \legend{APT,AugUCB,UCBE,UCBEV,CSAR,UA}
      	\end{axis}
      	\label{Fig:budgetExpt2}
        \end{tikzpicture}
    }
    \end{tabular}

	\begin{tabular}{cc}
	\centering
    \subfigure[0.32\textwidth][Expt-$3$: Three Group Setting (Gaussian)]
    {
    		\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
        %clip mode=individual,grid,grid style={gray!30},
       	grid=major,
       	clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
      	% UCB
		\addplot table{Chapter5/results/budgetTestGR1/APT1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR1/AugUCB1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR1/UCBEM1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR1/UCBEMV1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR1/SR1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR1/UA1_comp_subsampled.txt};
        \legend{APT,AugUCB,UCBE,UCBEV,CSAR,UA}
      	\end{axis}
      	\end{tikzpicture}
   		\label{Fig:budgetExpt3} 
    }
    &
    \subfigure[0.32\textwidth][Expt-$4$: Two Group Setting (Gaussian) ]
    {
    	\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
        %clip mode=individual,grid,grid style={gray!30},
		grid=major,
		clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
        % UCB
		\addplot table{Chapter5/results/budgetTestGR2/APT1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR2/AugUCBV1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR2/UCBEM1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR2/UCBEMV1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR2/SR1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR2/UA1_comp_subsampled.txt};
        \legend{APT,AUgUCB,UCBE,UCBEV,CSAR,UA}
        %\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc}
      	\end{axis}
      	\label{Fig:budgetExpt4}
        \end{tikzpicture}
    }
    \end{tabular}

	\begin{tabular}{cc}
    \subfigure[0.32\textwidth][Expt-$5$: Two Group Setting (Advance) ]
    {
    	\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
        %clip mode=individual,grid,grid style={gray!30},
		grid=major,
		clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
        % UCB
		\addplot table{Chapter5/results/budgetTestGR4/APT1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR4/AugUCB1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR4/UCBEM1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR4/UCBEMV1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR4/SR1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR4/UA1_comp_subsampled.txt};
        \legend{APT,AUgUCB,UCBE,UCBEV,CSAR,UA}
      	\end{axis}
      	\label{Fig:budgetExpt5}
        \end{tikzpicture}
    }
    &
    \subfigure[0.32\textwidth][Expt-$6$: Two Group Setting (Advance) ]
    {
    	\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
        %clip mode=individual,grid,grid style={gray!30},
		grid=major,
		clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=2} ]
        % UCB
		\addplot table{Chapter5/results/budgetTestGR3/testUCBEMV1_0.25_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR4/AugUCB1_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR3/testUCBEMV1_256_comp_subsampled.txt};
		\addplot table{Chapter5/results/budgetTestGR4/UCBEMV1_comp_subsampled.txt};
        \legend{UCBEV($0.25$), AugUCB, UCBEV($256$), UCBEV($1$)}
      	\end{axis}
      	\label{Fig:budgetExpt6}
        \end{tikzpicture}
    }
    \end{tabular}
    \caption{Performances of the various TBP algorithms in terms of error percentage vs. time-step, for  six different experimental scenarios.}
    \label{fig:budgetExpt}
    \vspace{-6mm}
\end{figure}
